The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-12-14 OA.tex
prepare for ecta submission
prepare for submission

\begin{center}
	\LARGE The limits of self-commitment and private paternalism \\[0.5em]
	\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
\end{center}

@@

\section{Treatment Explanation Materials and Pictures}
\vspace{.2in}

@@

\begin{figure}[H]
     \caption{Contract Terms Summary}
    \label{PaperSlip}
    \begin{center}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Receipt for client}
     %   \centering
        \includegraphics[width=0.65\textwidth]{Figuras/TicketLenderP.png}
    %\end{subfigure}

    %\vspace{3ex}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Personal promise signed by client}
     %   \centering
    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
    %\end{subfigure}
    \end{center}
    \scriptsize
        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity). We want to highlight the salience of some items. First the title clearly indicated which contract the client has (arrow 1). Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2). Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month. %The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient. It emphasizes that the client is giving his word, and that the promise is not a legal document.
\end{figure}

\begin{figure}[H]
     \caption{Explanatory Material}
    \label{ExplanatoryMaterial}
    \begin{center}
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/micas.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.
\end{figure}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
    \end{subfigure}
    \begin{subfigure}{0.415\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

@@

    \end{center}
    \scriptsize
        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. 
\end{figure}

@@

\vspace{.2in}

\normalsize
\linespread{1.25}
%Really force it to normal size and linespread
\normalsize
\linespread{1.25}

@@

\begin{table}[H]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\scriptsize
Translation of the baseline questionnaire.
\end{table}

\newpage
\subsection{Descriptives consistent with overconfidence}

\vspace{.2in}
\begin{figure}[H]
    \caption{Behavior of borrowers who lost their pawn}
    \label{proxy_naive}
    \begin{center}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.40\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.40\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize 
        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

\vspace{.1in}
\section{Internal Validity}

\begin{figure}[H]
     \caption{Box-plot across arms}
    \label{boxplot_attrition}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
    \caption{Number of pawns}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
    \caption{Number of borrowers}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms. The solid black line represent the median, while the gray line represent the mean. The dots on top of the box-plot represent an implicit CDF. 
\end{figure}

@@

\newpage
\section{Main treatment effects: Additional material}

\begin{landscape}
\subsection{Multiple loans}

@@

\begin{figure}[H]
    \caption{Determinants of choice}
    \label{determinants_choose}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

@@

\vspace{.2in}
\begin{figure}[H]
    \caption{Histogram of payments}
    \label{hist_payments}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{Status-quo}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Choice commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{subfigure}    
    \end{center}
     \scriptsize
     This figure shows the schedule of payments for each treatment arm. In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn. We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).

@@

Our main results, presented above, make no assumption on the default/recovery status of this loans. However, we compute the Financial Cost \& APR considering all the payments done so far. We now consider some alternative approaches. \\

@@

\vspace{.3in}
\begin{table}[H]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp.tex}}
}
\end{center}

\end{table}
 \scriptsize 
 Given the censored loans, i.e. loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm. Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}. Panel A, for instance, assumes that all outstanding loans are fully payed. Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default. Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B. Panel D assumes all remaining loans default. The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default. In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days. For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise. Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days. This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.

 Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome.

\begin{figure}[H]
        \caption{Interpolation on bounding censoring}
    \label{interpolation_censoring_imp}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
    \end{subfigure}     
    \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for Default }
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    \end{subfigure} 
    \end{center}
     \scriptsize  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels. We do not include the plot for financial cost, since for any imputation we still have significant results.

@@

\newpage
\section{Alternative explanations}

\vspace{.2in}
\subsection{Learning}
\normalsize
Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment. Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm. Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error. The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms. In each case, there is no statistically discernible difference in the rates of commitment take-up. Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation. For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment. This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow). The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two. Again, there is no statistically discernible difference in commitment take-up rates in either row. While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.

\vspace{.1in}
\begin{table}[H]
        \caption{Effect of Prior Assignment on Subsequent Choice}
    \label{learning_table}
\begin{center}
\scriptsize{\input{./Tables/learning_exp.tex}}
\end{center}
 \scriptsize

@@

\normalsize
\linespread{1.25}
%Really force it to normal size and linespread
\normalsize
\linespread{1.25}

\begin{comment}
\section{Causal Forest and individual predictions of `Mistakes'}

@@

\begin{figure}[H]
    \caption{Determinants sure confidence}
    \label{determinants_sure}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

@@

\section{Heterogeneity and Bounds}

@@

\vspace{.3in}
\begin{figure}[H]
    \caption{Fan \& Park bounds for benefit in APR\%}
    \label{fan_park_bounds}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize
    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
    This is greater than the share of borrowers who chose commitment: 11\%.
%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
\end{figure}

\vspace{.2in}
\begin{figure}[H]
        \caption{Empirical CDF: Forced commitment vs Control FOSF}
    \label{ecdf_fc}

>>>>

\begin{center}
	\LARGE The controlled choice design and private paternalism in pawnshop borrowing \\[0.5em]
	\Large{Appendix $-$ For Online Publication} \\[1em]
	\large \author{Craig McIntosh \and Isaac Meza \and Joyce Sadka \and Enrique Seira \and Francis J.\ DiTraglia}
\end{center}

@@

\linespread{1.05}

\linespread{1.05}

\section{ Treatment Explanation Materials and Pictures}
\vspace{.2in}

@@

\begin{figure}[H]
     \caption{Contract Terms Summary}
    \label{PaperSlip}
    \begin{center}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Receipt for client}
     %   \centering
        \includegraphics[width=0.5\textwidth]{Figuras/TicketLenderP.png}
    %\end{subfigure}

    %\vspace{3ex}
    %\begin{subfigure}{0.65\textwidth}
    %\caption{Personal promise signed by client}
     %   \centering
    %    \includegraphics[width=\textwidth]{Figuras/Personal Promise2.png}
    %\end{subfigure}
    \end{center}
    \scriptsize{
        We show a sample receipt that was given to clients that got assigned to the fee-forcing contract (the font and format were changed to protect Lender's P identity). We want to highlight the salience of some items. First the title clearly indicated which contract the client has (arrow 1). Second, in the case of the fee contract it clearly indicates that there is a fee for paying late equivalent to 2\% of the value of the monthly payment (arrow 2). Third, there is a calendar for payments clearly specifying the dates and amounts to pay each month. %The bottom panel of the figure shows a ``promise slip'', the paper that those who were assigned (or chose) to the monthly payment with promise had to sign to make the promise salient. It emphasizes that the client is giving his word, and that the promise is not a legal document.
        }
\end{figure}

\begin{figure}[H]
     \caption{Explanatory Material}
    \label{ExplanatoryMaterial}
    \begin{center}
        \centering
        \includegraphics[width=0.6\textwidth]{Figuras/micas.pdf}

    \end{center}
    \scriptsize{
        This is a (translated) sample information slide shown to clients. The real ones were twice the size of this figure and were laminated. Different ones were shown for each treatment arm.}
\end{figure}

@@

    \begin{subfigure}{0.45\textwidth}
    \caption{Pawnshop}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio2_.png}
    \end{subfigure}
    \begin{subfigure}{0.415\textwidth}
    \caption{Lost pawns which are for sale}
        \centering
        \includegraphics[width=\textwidth]{Figuras/empenio3_.png}
    \end{subfigure}
    \end{center}
    \scriptsize{
        This figure  shows pictures of pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality.} 
\end{figure}

@@

    \end{center}
    \scriptsize{
        This figure shows pictures of gold buyers next to pawnshops in Mexico city. They do not necessarily coincide with Lender P for confidentiality. }
\end{figure}

@@

\normalsize
\linespread{1.05}
%Really force it to normal size and linespread
\normalsize
\linespread{1.05}

@@

\begin{table}[H]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\scriptsize{
Translation of the baseline questionnaire.}
\end{table}

\newpage
\subsection{More descriptives}

%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.

%Of those who renew, 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn. Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}

\begin{figure}[!h]
\caption{Financial cost.}
  \label{fc_hist}
    \begin{center}
    \begin{subfigure}{.42\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
        \caption{}
    \end{subfigure}
     \begin{subfigure}{0.42\textwidth}
       \centering
      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
      \caption{}
    \end{subfigure}
    \end{center}

 \scriptsize{Panel (a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn. Panel (b) shows the analogous histogram for the APR.
%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost. Most of the APR costs indeed come from clients who do not recover their pawn.}

      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
\end{figure}

\begin{figure}[!h]
    \caption{Behavior of borrowers who lost their pawn}
    \label{proxy_naive}
    \begin{center}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to first payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_firstdays_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Elapsed days to last payment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_days_default.pdf}
    \end{subfigure}
        \begin{subfigure}{0.35\textwidth}
        \caption{Payments as \% of loan}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_percpay_default.pdf}
    \end{subfigure}
    \begin{subfigure}{0.35\textwidth}
        \caption{Number of payments}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_numpay_default.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize 
        This figure provides more details on the behavior of clients who were assigned to the control group and did not recover their pawn. Panel (a) shows a histogram of days elapsed from the pawn to the first payment, while panel (b) displays a histogram of days elapsed until the last payment. Some borrowers make payments after day 105, the end of the grace period: if they pay all interest owed, they can ``restart'' the loan. This amounts to starting a new loan with the same conditions and same pawn. Panel (c) shows a histogram of the fraction of the loan paid, while panel (d) presents a barplot of the number of times that borrowers went to the branch to make payments.
      %\textit{Do file: }  \texttt{hist\_den\_default.do}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\section{ Internal Validity}

If potential borrowers disliked being forced into a commitment contract, we would expect a lower number of pawns on branch days where only the commitment contract is available compared to control days. Table \ref{attrition_table} shows that this is not the case. There is no difference at all between the Control and Forced Commitment arm in terms of the number of pawns per branch-day. Although we cannot reject equality across the three arms (p-value=0.21), the Choice arm appears to have a somewhat larger number of borrowers than the Control and Forced arms.\footnote{p-value=0.23 and 0.12 respectively.} This seems to be due to sampling variability. The differences across arms are smaller when we look at medians, or when we look at the number of borrowers pawning (some borrowers pawn more than one piece). Figure \ref{boxplot_attrition} shows that full distribution of loans per day is very similar across treatment arms. The only noticeable difference is that the choice arm has a few more positive outliers.\footnote{If we winzorize at the 90th percentile, the mean number of branch-day pawns becomes identical across arms.}

\begin{table}
\caption{Limited and balanced attrition}
\label{attrition_table}
\begin{center}
\scriptsize{\input{./Tables/Attrition.tex}}
\end{center}
\scriptsize{Each row in this table 
 corresponds to a regression. The dependent variables are: the number of pawns-loans originated per day per branch, the number of borrowers per day-branch, a variable indicating whether a person who answered the baseline survey (before knowing contract terms) ended up pawning, and an indicator of whether the person that obtained the loan answered the baseline survey. Each dependent variable is regressed in a multivariate OLS regression against the experimental arms indicators (control, forced commitment, choice). The table reports the coefficients on each of these indicators, as well as the p-value of an F-test of the null hypothesis of equality of the three coefficients. Figure \ref{boxplot_attrition}, in the appendix shows a box-plot of the first two variables, showing the distribution across arms is balanced.}
%\textit{Do file: } \texttt{ss\_att.do}
\end{table}

The bottom panel of Table \ref{attrition_table} shows balance in a more focused way, given that the surveys were conducted prior to the revelation of treatment status. We find that in no arm did more than three percent of individuals who responded to the survey go on to refuse loans. That is, the overwhelming marjority of potential borrowers did not leave the branch after learning which contract was on offer. Moreover, the extremely small fraction that did leave is balanced across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

A less critical form of attrition is differential refusal to answer the survey questions.  The survey was conducted before treatment status was revealed, and we observe loan outcomes regardless of whether the survey was conducted.  Our core experimental estimates do not use the survey data as covariates, but the analysis in Section \ref{Paternalism} is restricted to the subset of borrowers who answered at least some survey questions. The bottom row of Table \ref{attrition_table} shows that the survey response rate is broadly similar across arms (about 78 percent).

\vspace{.2in}
\begin{figure}[H]
     \caption{Box-plot across arms}
    \label{boxplot_attrition}
    \begin{center}
    \begin{subfigure}{0.35\textwidth}
    \caption{Number of pawns}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
        \begin{subfigure}{0.35\textwidth}
    \caption{Number of borrowers}
        \centering
        \includegraphics[width=\textwidth]{Figuras/box_plot_num_pawns.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize
        This figure presents box-plot for the number of pawns and borrowers per branch-day across different arms. The solid black line represent the median, while the gray line represent the mean. The dots on top of the box-plot represent an implicit CDF. 
\end{figure}

@@

\begin{landscape}
\section{ Main treatment effects: Additional material}
\subsection{Multiple loans}

@@

\begin{figure}[H]
    \caption{Determinants of choice}
    \label{determinants_choose}
    \begin{center}
    \begin{subfigure}{0.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

@@

\begin{figure}[H]
    \caption{Histogram of payments}
    \label{hist_payments}
    \begin{center}
    \begin{subfigure}{0.31\textwidth}
        \caption{Status-quo}
        \centering
    \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{subfigure}
    \begin{subfigure}{0.31\textwidth}
        \caption{Forced commitment}
        \centering
    \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.31\textwidth}
        \caption{Choice commitment}
        \centering
    \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{subfigure}    
    \end{center}
     \scriptsize
     This figure shows the schedule of payments for each treatment arm. In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn. We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).

@@

Our main results, presented above, make no assumption on the default/recovery status of this loans. However, we compute the Financial Cost \& APR considering all the payments done so far. We now consider some alternative approaches.

@@

\begin{table}[H]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{1.0\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp_1.tex}}
}
\end{center}

\end{table}
\begin{table}[H]
\begin{center}
\resizebox{1.0\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp_2.tex}}
}
\end{center}

 \scriptsize {
 Given the censored loans, i.e. loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm. Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}. Panel A, for instance, assumes that all outstanding loans are fully payed. Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default. Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B. Panel D assumes all remaining loans default. The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default. In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days. For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise. Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days. This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.

\noindent Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome. }
\end{table}

\begin{figure}[H]
        \caption{Interpolation on bounding censoring for Default}
    \label{interpolation_censoring_imp}
    \begin{center}
   % \begin{subfigure}{0.49\textwidth}
   % \caption{Significance area for APR}
   %      \centering
   %      \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
   %  \end{subfigure}     
   %  \begin{subfigure}{0.49\textwidth}
   % \caption{Significance area for Default }
        \centering
        \includegraphics[width=0.5\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    % \end{subfigure} 
    \end{center}
     \scriptsize  {The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels. We do not include the plot for APR nor financial cost, since for any imputation we still have significant results.}

@@

\subsection{Robustness accounting for other costs}

\begin{table}[!h]
\caption{Effects on more comprehensive cost measures}
\label{table_robustness_fc}
\begin{center}
\scriptsize{\input{./Tables/fc_robustness.tex}}
\end{center}
 \scriptsize{ This table augments the measure of financial cost presented in Table \ref{main_impact_table} with measures of transaction costs, subjective costs, and adjustments for liquidity costs. Panel A reports financial cost in pesos, while Panel B shows APR. Columns (1) and (6) replicate our previous results for comparability. Columns (2) and (7) of Table \ref{table_robustness_fc} use the subjective value of the pawn reported by the borrower rather than its appraised value. Columns (3) and (8) adjust for self-reported transport costs per visit plus an entire day's wage, both multiplied by the number of visits that each individual made.\footnote{For clients who did not complete the individual survey, we adjust using the mean self-reported transport cost among respondents of the respective branch.} Columns (4) and (9) adjust to consider the liquidity cost. Finally, columns (5) and (10) include all three changes together. The main takeaway from the table is that results are quite robust to including a much expanded measure of costs. Each regression includes branch and day-of-week FE. Standard errors are clustered at the branch-day level.}
%\textit{Do file: } \texttt{fc\_robustness.do}
\end{table}

\section{ Alternative explanations}

\subsection{Learning}
\normalsize
Table \ref{learning_table} presents information about borrowers' \emph{future} pawning behavior as a function of treatment assignment. Column (1) considers the 228 clients who returned only a second time to pawn again at a day/branch that was randomly assigned to the choice arm. Each of the two rows in this column presents a difference of mean commitment take-up rates, and associated standard error. The first row compares those who were \emph{initially} assigned to forced commitment against those where were assigned to control; the second row compares those who were initially assigned to the choice commitment arm to those who were assigned to the other two arms. In each case, there is no statistically discernible difference in the rates of commitment take-up. Granted, this is a selected sample because the decision to pawn again is potentially endogenous to the initial treatment allocation. For this reason, Column (2) considers the full sample of 4441 borrowers by re-defining the outcome variable to be an indicator for returning to pawn again at a branch/day when commitment was offered \emph{and} choosing commitment. This composite outcome variable is not subject to the sample selection problem (although it is directly driven by the decision to repeat borrow). The comparison in the two rows remains the same: forced commitment versus control in row one and choice commitment versus forced arms in row two. Again, there is no statistically discernible difference in commitment take-up rates in either row. While these exercises cannot completely exclude the possibility that learning plays a role, they provide no indication that the lack of voluntary compliance is simply a matter of inexperience with commitment.

\vspace{.1in}
\begin{table}[!h]
        \caption{Effect of Prior Assignment on Subsequent Choice}
    \label{learning_table}
\begin{center}
\scriptsize{\input{./Tables/learning_exp.tex}}
\end{center}
 \scriptsize

@@

\normalsize
\linespread{1.05}
%Really force it to normal size and linespread
\normalsize
\linespread{1.05}

\begin{comment}
\section{ Causal Forest and individual predictions of `Mistakes'}

@@

\begin{figure}[H]
    \caption{Determinants sure confidence}
    \label{determinants_sure}
    \begin{center}
    \begin{subfigure}{0.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

@@

\section{ Heterogeneity and Bounds}

@@

\begin{figure}[!h]
    \caption{Fan \& Park bounds for benefit in APR\%}
    \label{fan_park_bounds}
    \begin{center}
    \begin{subfigure}{0.55\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/fan_park_bounds_apr.pdf}
    \end{subfigure}
    \end{center}
        \scriptsize
    This figure depicts the \cite{fan2010sharp} bounds on the distribution $F_\Delta$ of individual treatment effects $\Delta \equiv (Y_1 - Y_0)$, described in Section \ref{sec:bounds}, for the APR outcome.
    The dark red curve and light red shaded region give the estimated upper bound function $\overline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval. 
    The dark blue curve and light blue shaded region give the estimated lower bound function $\underline{F}$ for $F_\Delta$ and associated (pointwise) 95\% confidence interval.
    Confidence intervals are computed using the asymptotic distribution for the bounds. See \cite{fan2010sharp} for details.
    The bounds are pointwise sharp: at any specified value of $\delta$ the bounds $\underline{F}(\delta) \leq F_\Delta(\delta) \leq \overline{F}(\delta)$ cannot be improved without imposing additional assumptions.
    Evaluating the bounds at $\delta = 0$, we see that between 23\% and 97\% of borrowers have a positive individual treatment effect.
    This is greater than the share of borrowers who chose commitment: 11\%.
%\textit{Do file: } \texttt{fan\_park\_bnds.do}       
\end{figure}

\begin{figure}[!h]
        \caption{Empirical CDF: Forced commitment vs Control FOSF}
    \label{ecdf_fc}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
         \caption{APR benefit}
         \centering
         \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
     \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure plots the empirical CDF of experimental outcomes separately for the control (status quo) in dashes, and forced commitment contracts (solid). In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit. 
    The empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo. This can be seen by examining the dotted line, which shows the difference $(\text{Control} - \text{Commitment})$. 
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{fosd_ecdf.do}}
\end{figure}

\begin{figure}
        \caption{Distribution of treatment effects under rank invariance.}
    \label{te_rankinvariance}
